pirouette: Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-04-02 article.tex
Updates from Overleaf

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{workflow.png}
  \caption{
    \texttt{pirouette} pipeline. 
    The pipeline starts from a phylogeny (1a) simulated by generative prior 
$\mathit{P}$.
    The phylogeny is converted to an alignment (2a) using alignment model 
$\mathit{A}$. 
    The user supplies one or more experiments.
    For each candidate experiment $\mathit{X}$ 
    (a tuple of inference model $\mathit{I}$ and condition $\mathit{C}$),
    if its condition $\mathit{C}$ is 
    satisfied (which can depend on the alignment), 
    it becomes a selected experiment $\mathit{X'}$, 
    to be used in the next step (3a).
    The inference models of the selected experimenst use the alignment (2a) 
    to each create a Bayesian posterior of (parameter estimates and) 
    phylogenies (4a). 
    Each of the posteriors' trees is compared to the true phylogeny (1a) 
    using error measure $\mathit{E}$, 
    resulting in an error distribution (5a). 
    Optionally, a twin phylogeny (1b) can be generated from the original 
    phylogeny (1a) using twinning parameters $T$, where $T$ may depend on
    the experiments \richel{improve}.
    From a twin phylogeny, the same intermediate steps are taken,
    resulting in a twin error distribution (5b)
    \giovanni{Ok, that's my take on this: 1) all the capital letters should go 
in a ball (or a rhombus, as you already did for C) which stands in the middle 
of the arrows (as with C now); 2) The box in the middle should contain all the 
inference models $I_{i}$; 3) We need another C at the intersection of the 
arrows that point to T and A; 4) In between of the arrow 2a->4a there should be 
another rhombus (or circle) with an I (or I' or I*, according on how we want to 
call the selected inference model), which is pointed by the rhombus (of circle) 
containing C; 5) The first arrow should start from a rhombus (or circle) with P 
inside.}
  }
  \label{fig:pipeline}
\end{figure}

@@

If, instead, there is no preference for a specific tree prior, the user can let 
\verb;pirouette; select the best inference model from a list of candidate 
models. The model selection is performed automatically based on the criterion 
of the highest evidence (aka marginal likelihood). This option can be specified 
providing any number of experiments, selecting "model\_type" to be "candidate" 
for each of them, and "run\_if" to be "best\_candidate" (table~\ref{tab:RQ2} 
will summarize this for ERQ 2).

@@

Setting up experiments like this is thought to be so common,
that \verb;pirouette; has a simple function to do:
\verb;create_all_experiments; will create the entire set of 40 experiments,
containing the inference models of all combinations of 4 site 
models, 2 clock models and 5 tree priors.

@@

We can run the \verb;pirouette; method with listing~\ref{lst:pir_run}
and plot the results with listing~\ref{lst:pir_plot}.
The resulting figure is shown in figure~\ref{fig:example_2}.

@@

In ERQ 1 we measured the baseline error of the \verb;pirouette; method, 
by using a standard tree prior in both the generation of the tree 
and in our inference.
The goal of \verb;pirouette; is to quantify the 
influence of a new (non-standard) tree prior.
To do so, we need to compare the inference error 
from the new tree prior to a baseline error,
by use of a twin tree (see subsection~\ref{subsec:twinning}).
To do so, we use the twin tree as a control for the main pipeline.
In this example, we do not know the generative tree prior $\mathit{P}$,
but we do know the alignment model, $\mathit{A}$.
In this ERQ, we assume the new tree prior is so closely related to
a standard tree prior, that it is reasonable to hand-pick a standard tree prior 
to serve as a stand-in generative tree prior.

@@

Most of the settings for this example research question are
the same as in the previous section, which are
the phylogeny from an unknown speciation model 
(listing~\ref{lst:unknown_phylogeny}), 
the alignment parameters (listing~\ref{lst:create_alignment})
and the list of experiments (listing~\ref{lst:create_generative_experiment}),
the latter stating that the generative tree prior is a Yule tree prior.

This time, however, we are interested measuring both the inference error
and a baseline error, which is achieved by creating a twinning parameter
set. 
This time, however, we are interested in creating a twin tree. A twin tree
has the same topology as the given tree, yet its branching times are simulated 
according to the standard tree prior used by BEAST2 to produce the posterior 
for the main pipeline. 
Since there is coherence between the inference model and the generative model, 
we expect BEAST2 to produce a posterior of phylogenies more similar to the 
original one, respect to the outcome of the main pipeline. 
Due to this, the twinning process is used to provide a control for the main 
experiment.

Creating a twinning parameter is easy, as it has sensible default settings.
For clarity, we explicitly show the default values of the most
important arguments:

@@

Bundling all the \verb;pirouette; arguments by \verb;create_pir_params;:

@@

Running and plotting the results:

@@

The resulting figure is shown in figure~\ref{fig:example_3}

@@

@@

To answer ERQ 2 we used an evidence-based model selection procedure to obtain 
an 
error distribution.
However, it is unclear to what extent this error is due to the mismatch between 
the tree priors (from generative and inference models) or due to stochasticity. 
As mentioned in ERQ 1, \verb;pirouette; provides a tool to evaluate this, using 
the twinning process. We now apply it to the same pipeline followed in ERQ 2.
This leads to our fourth example research question:

"What is the error made by BEAST2 from a phylogeny 
derived from an unknown speciation model,
when selecting the best inference model, 
in relationship to the background error?"

@@

Here, same as example 2 and 3, we start with the phylogeny 
from an unknown speciation model (listing~\ref{lst:unknown_phylogeny}), 
The first step in \verb;pirouette; is to simulate a DNA alignment 
from the given phylogeny, for which we will use the same code 
as shown in listing~\ref{lst:create_alignment}.

We again specify we want all 40 inference models to compete, 
by calling \verb;create_all_experiments;,
as done in listing~\ref{lst:create_all_experiments}.

We again pick to use the default setup to measure the error,
as shown in listing~\ref{lst:create_error_measure_params}.

To get an idea of a baseline error made by BEAST2, 
we also make use of the twinning option by using the
default created twinning parameters, as shown in 
listing~\ref{lst:create_twinning_params}.

@@

Running the experiment:

@@

Again, showing the results:

@@

The resulting figure is shown in figure~\ref{fig:example_4}.

@@

@@

In ERQs 1 and 2 we used \verb;pirouette; to  
run the analysis on the main pipeline, either using a 'generative' or a 
'best\_candidate' inference model, resulting in one error distribution,
that does not mean much on its own.
In ERQs 3 and 4 we measure the baseline error caused by stochasticity,
by running a parallel twin pipeline, resulting in two error distributions:
the baseline error and the complete inference error.
We can sum up all \verb;pirouette;'s features presented so far in the fifth 
research question:

"What is the error made by BEAST2 from a phylogeny, 
when the generative model is hand-picked, 
compared to candidates with similar inference models, 
in relationship to the background error?"

@@

In this example, we use a tree generated by the Yule process.
Instead of using the common Yule tree as in example 1, we'll use
a Yule tree of low (actually: zero) likelihood: 
the one as used in ERQs 2-4, by using the code shown 
in listing~\ref{lst:unknown_phylogeny}.
The first step in \verb;pirouette; is to simulate a DNA alignment 
from the given phylogeny, for which we will use the same code 
as shown in listing~\ref{lst:create_alignment}.

@@

Specifying all candidates can be done simply by calling 
\verb;create_all_experiments; and excluding the generative inference model,
resulting in 39 candidate experiments:

@@

\begin{lstlisting}[language=R, floatplacement=H, frame=single]
experiments <- c(list(generative_experiment), candidate_experiments)
\end{lstlisting}

@@

Running the experiment in the usual fashion:

@@

Again, showing the results:

@@

The resulting figure is shown in figure~\ref{fig:example_5}.

@@

\begin{table}
  \begin{tabular}{ | r | c | c | c | }
    \hline
    \textbf{Compare with} & \textbf{E2} & \textbf{E3} & \textbf{E4} \\ 
    \hline
    \textbf{E1} & Y & Y & N \\
    \textbf{E2} & . & N & Y \\
    \textbf{E3} & . & . & Y \\
    \textbf{E4} & . & . & . \\
    \hline
  \end{tabular}
  \caption{
    Error distributions that are relevant to compare.
    E1: true tree, generative model.
    E2: true tree, best candidate model.
    E3: true tree, generative model.
    E4: true tree, best candidate model.
  }
  \label{tab:relevant_comparisions}
\end{table}

\begin{table}
  \begin{tabular}{ | r | c | p{9cm} | }
    \hline
    \textbf{Condition} & \textbf{Expectation} & \textbf{Interpretation} \\ 
    \hline
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E1 > E2$}       & Unexpected & Novel tree prior is more related to 
      best candate than hand-picked tree prior \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E1 \approx E2$} & Possible   & Hand-picked tree prior is just as 
      suitable as the best candidate tree prior \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E1 < E2$}       & Expected   & Hand-picked tree prior is the most 
      related tree prior \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hline
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E1 > E3$}       & Unknown    & Novel tree prior important \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E1 \approx E3$} & Unknown    & Novel tree prior unimportant \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E1 < E3$}       & Unexpected & Twinning procedure increases 
      inference errors when using hand-picked tree prior \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hline
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E2 > E4$}       & Expected   & Impact of novel tree prior cannot 
      be compensated for by model selection: twin tree with low likelihood? \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E2 \approx E4$} & Possible   & Best candidate tree priors perform 
      equally well in true and twin tree: true and twin tree similar? \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E2 < E4$}       & Unexpected & Twinning procedure increases 
      inference errors  when using best tree prior candidate \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hline
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E3 > E4$}       & Unexpected & Hand-picked tree prior (that equals 
      the twinning tree prior!) worse than best candidate tree prior \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E3 \approx E4$} & Possible   & Twin tree fits equally well to the 
      hand-picked and best candidate tree prior  \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E3 < E4$}       & Expected   & Hand-pick tree prior (that equals 
      the twinning tree prior) performs as expected \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hline
  \end{tabular}
  \caption{
    Interpretation of the different error distributions.
    This assumes that the operators ($<$, $\approx$ and $>$) to compare
    distributions are defined.
    E1: true tree, generative model.
    E2: true tree, best candidate model.
    E3: true tree, generative model.
    E4: true tree, best candidate model.
  }
  \label{tab:interpretation}
\end{table}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{workflow.png}
  \caption{
    \texttt{pirouette} pipeline. 
    The pipeline starts from a phylogeny (1a) simulated by generative prior 
$\mathit{P}$.
    The phylogeny is converted to an alignment (2a) using alignment model 
$\mathit{A}$. 
    The user supplies one or more experiments.
    For each candidate experiment $\mathit{X}$ 
    (a tuple of inference model $\mathit{I}$ and condition $\mathit{C}$),
    if its condition $\mathit{C}$ is 
    satisfied (which can depend on the alignment), 
    it becomes a selected experiment $\mathit{X'}$, 
    to be used in the next step (3a).
    The inference models of the selected experiment use the alignment (2a) 
    to each create a Bayesian posterior of (parameter estimates and) 
    phylogenies (4a). 
    Each of the posteriors' trees is compared to the true phylogeny (1a) 
    using error measure $\mathit{E}$, 
    resulting in an error distribution (5a). 
    Optionally, a twin phylogeny (1b) can be generated from the original 
    phylogeny (1a) using twinning parameters $T$, where $T$ may depend on
    the experiments \richel{improve}.
    From a twin phylogeny, the same intermediate steps are taken,
    resulting in a twin error distribution (5b)
    \giovanni{Ok, that's my take on this: 1) all the capital letters should go 
in a ball (or a rhombus, as you already did for C) which stands in the middle 
of the arrows (as with C now); 2) The box in the middle should contain all the 
inference models $I_{i}$; 3) We need another C at the intersection of the 
arrows that point to T and A; 4) In between of the arrow 2a->4a there should be 
another rhombus (or circle) with an I (or I' or I*, according on how we want to 
call the selected inference model), which is pointed by the rhombus (of circle) 
containing C; 5) The first arrow should start from a rhombus (or circle) with P 
inside.}
  }
  \label{fig:pipeline}
\end{figure}

@@

If, instead, there is no preference for a specific tree prior, the user can let 
\verb;pirouette; select the best inference model from a list of candidate 
models. The model selection is performed automatically based on the criterion 
of the highest evidence (also known as marginal likelihood). This option can be specified 
providing any number of experiments, selecting "model\_type" to be "candidate" 
for each of them, and "run\_if" to be "best\_candidate" (table~\ref{tab:RQ2} 
will summarize this for ERQ 2).

@@

As model selection is commonly performed on the full list of available candidate models,
\verb;pirouette; has a dedicated function to provide it:
\verb;create_all_experiments; will create the entire set of 40 experiments,
containing the inference models of all combinations of 4 site 
models, 2 clock models and 5 tree priors.
\giovanni{Do we still want to use CBS, CCP and CEP?}

@@

We can now run \verb;pirouette;  with listing~\ref{lst:pir_run}
and plot the results with listing~\ref{lst:pir_plot}.
The resulting figure is shown in figure~\ref{fig:example_2}.

@@

In ERQ 1 we measured the baseline error of the \verb;pirouette; method. We did so by using a standard tree prior to generate the original tree as well as in the inference.
The goal of \verb;pirouette; is to quantify the 
influence of a new (non-standard) tree prior.
To do so, we need to compare the inference error 
from the new tree prior to a baseline error,
by using a twin tree (see subsection~\ref{subsec:twinning}).
To do so, we use the twin tree as a control for the main pipeline.
In this example, we have no knowledge of the generative tree prior $\mathit{P}$
but we know the alignment model $\mathit{A}$.
In this ERQ it is reasonable to hand-pick a standard tree prior 
to serve as a stand-in generative tree prior as we assume that they are closely related.

@@

Most of the settings for this ERQ are
the same as in the previous section. They are
the phylogeny from an unknown speciation model 
(listing~\ref{lst:unknown_phylogeny}), 
the alignment parameters (listing~\ref{lst:create_alignment})
and the list of experiments (listing~\ref{lst:create_generative_experiment}),
the latter stating that the generative tree prior is a Yule tree prior.

This time, however, we are interested in measuring both the inference error
and a baseline error. We do so by setting the twinning parameters $\mathit{T}$ to create a twin tree. A twin tree
has the same topology as the given tree, yet its branching times are simulated 
according to the standard tree prior used by BEAST2 to produce the posterior 
for the main pipeline. 
Since there is coherence between the inference model and the generative model, 
we expect BEAST2 to produce a posterior of phylogenies that are more similar to the 
original one, respect to the outcome of the main pipeline. 
Due to this, the twinning process is used to provide a control for the main 
experiment.

Creating the twinning parameters is easy, as it has sensible default settings.
For the sake of clarity, we explicitly show the default values of the most
important arguments:

@@

We bundle again all the \verb;pirouette; arguments using \verb;create_pir_params;:

@@

Finally, we run and plot the results:

@@

The output is shown in figure~\ref{fig:example_3}

@@

To answer ERQ 2 we used an evidence-based model selection procedure to obtain 
an 
error distribution.
However, it is unclear to what extent this error is due to the mismatch between 
the tree priors (from generative and inference models) or due to stochasticity. 
As mentioned in ERQ 1, \verb;pirouette; provides a tool to evaluate this, using 
the twinning process. We now apply it to the same pipeline followed in ERQ 2.

@@

"What is the error made by BEAST2 from a phylogeny 
derived from an unknown speciation model,
when selecting the best inference model, 
in relation to the background error?"

@@

Here, as in examples 2 and 3, we start with the phylogeny 
generated by an unknown speciation model (listing~\ref{lst:unknown_phylogeny}). 
The first step in \verb;pirouette; is to simulate a DNA alignment 
from the given phylogeny, for which we will use the same code 
as shown in listing~\ref{lst:create_alignment}.

We specify that we want all 40 inference models to compete 
by calling \verb;create_all_experiments;,
as we previously did in listing~\ref{lst:create_all_experiments}.

We choose again to use the default error measurement setup,
as shown in listing~\ref{lst:create_error_measure_params}.

To get an idea of a baseline error made by BEAST2, 
we also make use of the twinning option by using the
default twinning parameters, as shown in 
listing~\ref{lst:create_twinning_params}.

@@

We run the experiment:

@@

and show the results:

@@

The output is shown in figure~\ref{fig:example_4}.

@@

In ERQs 1 and 2 we used \verb;pirouette; to  
run the analysis on the main pipeline, either using a 'generative' or a 
'best\_candidate' inference model, resulting in one error distribution,
that does not mean much on its own.
In ERQs 3 and 4 we measured the baseline error caused by stochasticity,
by running a parallel twin pipeline. This yielded two error distributions:
the baseline error and the complete inference error.

@@

"What is the error made by BEAST2 from a phylogeny, 
when the generative model is hand-picked, 
compared to candidates with similar inference models, 
in relation to the background error?"

@@

In this example, we use a tree generated by the Yule process.
Instead of using the common Yule tree as in example 1, we will use
a Yule tree of low (actually: zero) likelihood: 
the one as used in ERQs 2-4, by using the code shown 
in listing~\ref{lst:unknown_phylogeny}.
The first step in \verb;pirouette; is to simulate a DNA alignment 
from the given phylogeny, for which we will use the same code 
as shown in listing~\ref{lst:create_alignment}.

@@

We can specify all the candidates simply by calling 
\verb;create_all_experiments; and excluding the generative inference model,
resulting in 39 candidate experiments:

@@

\begin{lstlisting}[language=R, floatplacement=H, frame=single]
experiments <- c(list(generative_experiment), candidate_experiments)
\end{lstlisting}
\giovanni{Does this code actually work?}

@@

We run the experiment in the usual fashion:

@@

We plot the results:

@@

The output is shown in figure~\ref{fig:example_5}.

@@

\begin{table}
  \begin{tabular}{ | r | c | c | c | }
    \hline
    \textbf{Compare with} & \textbf{E2} & \textbf{E3} & \textbf{E4} \\ 
    \hline
    \textbf{E1} & Y & Y & N \\
    \textbf{E2} & . & N & Y \\
    \textbf{E3} & . & . & Y \\
    \textbf{E4} & . & . & . \\
    \hline
  \end{tabular}
  \caption{
    Error distributions that are relevant to compare.
    E1: true tree, generative model.
    E2: true tree, best candidate model.
    E3: true tree, generative model.
    E4: true tree, best candidate model.
    \giovanni{What if instead we use two letters, such as "TG", "TB", "WG", "WB"?}
    \giovanni{There is a typo: true tree is everywhere and twin is not present.}
  }
  \label{tab:relevant_comparisions}
\end{table}

\begin{table}
  \begin{tabular}{ | r | c | p{9cm} | }
    \hline
    \textbf{Condition} & \textbf{Expectation} & \textbf{Interpretation} \\ 
    \hline
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E1 > E2$}       & Unexpected & Novel tree prior is more related to 
      best candidate than hand-picked tree prior \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E1 \approx E2$} & Possible   & Hand-picked tree prior is just as 
      suitable as the best candidate tree prior \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E1 < E2$}       & Expected   & Hand-picked tree prior is the most 
      related tree prior \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hline
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E1 > E3$}       & Unknown    & Novel tree prior important \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E1 \approx E3$} & Unknown    & Novel tree prior unimportant \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E1 < E3$}       & Unexpected & Twinning procedure increases 
      inference errors when using hand-picked tree prior \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hline
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E2 > E4$}       & Expected   & Impact of novel tree prior cannot 
      be compensated for by model selection: twin tree with low likelihood? \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E2 \approx E4$} & Possible   & Best candidate tree priors perform 
      equally well in true and twin tree: true and twin tree similar? \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E2 < E4$}       & Unexpected & Twinning procedure increases 
      inference errors  when using best tree prior candidate \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hline
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E3 > E4$}       & Unexpected & Hand-picked tree prior (that equals 
      the twinning tree prior!) worse than best candidate tree prior \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E3 \approx E4$} & Possible   & Twin tree fits equally well to the 
      hand-picked and best candidate tree prior  \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \textbf{$E3 < E4$}       & Expected   & Hand-pick tree prior (that equals 
      the twinning tree prior) performs as expected \\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \hline
  \end{tabular}
  \caption{
    Interpretation of the different error distributions.
    This assumes that the operators ($<$, $\approx$ and $>$) to compare
    distributions are defined.
    E1: true tree, generative model.
    E2: true tree, best candidate model.
    E3: true tree, generative model.
    E4: true tree, best candidate model.
  }
  \label{tab:interpretation}
\end{table}
